\documentclass[12pt]{article}
\usepackage{algos-tasks}

\DeclareMathOperator{\HamDist}{\mathsf{HammingDist}}
\DeclareMathOperator{\BothZero}{\mathsf{BothZero}}
\DeclareMathOperator{\BothOne}{\mathsf{BothOne}}

\begin{document}
\task[regular]{Hamming Distance}

\begin{question}
For two arrays $A$ and $B$ of $n$ binary integers, the {\em Hamming distance} of $A$ and $B$ is the number of indices where $A$ and $B$ disagree. For example, if $A = [1, 1, 0, 1]$ and $B = [0, 1, 1, 1]$, then the Hamming distance of $A$ and $B$ is 2 since $A$ and $B$ disagree at indices 1 and 3.

Let $P[1..m]$ be an array of $m$ binary integers and $T[1..n]$ an array of $n$ binary integers, where $m \leq n$. Design and analyse an $O(n \log n)$ algorithm to return the minimum Hamming distance between $P$ and a subarray of $T$ of length $m$.

For example, consider the following pattern array $P = [1, 1, 0, 1, 0]$ and the corresponding text array $T = [\textcolor{black!30}{0, 0, } \textcolor{red!80}{\underline{1, 1, 0, 0, 0}}\textcolor{black!30}{, 1, 0}]$: the minimum Hamming distance is 1 with the subarray highlighted.

{\bfseries Hint.} {\em For a subarray $S$ of length $m$, the Hamming distance is given by} \[\HamDist(S) = m - \BothOne(S) - \BothZero(S),\] where the last two terms indicate the number of places where subarray $S$ and the pattern are both one or both zero respectively.
\end{question}

\begin{rubric}
    \begin{itemize}
    \item Your response should describe the steps followed to execute the algorithm in simple English. Do not write a program, and do not transcribe a program back to written English.
    
    You \textbf{must} justify the correctness of your algorithm.
    
    You \textbf{must} justify that your algorithm runs in time complexity that you claim.
\end{itemize}
Expected response length: about one page.
\end{rubric}

\begin{solution}
\end{solution}

\begin{attribution}
\end{attribution}

\end{document}