\documentclass[12pt]{article}
\usepackage{algos-tasks}

\begin{document}
\task[regular]{Diameter of a Tree II}

\begin{question}
Recall from Diameter of a Tree I:
\begin{quote}
    Let $T = (V,E)$ be an unweighted tree (an undirected, connected, acyclic graph) with $n$ vertices. For two vertices $u,v \in V$, the \textit{distance} between $u$ and $v$ (denoted $d(u,v)$) is the length of the shortest path (by number of edges) between $u$ and $v$. The {\em diameter} $D$ of $T$ is the greatest distance between any two vertices in $T$. That is,
\[ D = \max_{u,v\in V} d(u,v). \]

We distinguish between {\em the} diameter and {\em a} diameter; the former is defined as above, and the latter is a path in $T$ with length $D$.
\end{quote}
Recall also from Diameter of a Tree I that the following algorithm also correctly finds {\em the} diameter of a tree:
    \begin{quote}
        Select an arbitrary vertex $r \in V$. 
        
        Run a BFS from $r$ and find the furthest vertex from $r$, denote this vertex $x$. 
        
        Run a BFS from $x$ and find the furthest vertex from $x$, denote this vertex $y$. 
        
        $x \rightarrow y$ is {\em a} diameter of the tree, with length $d(x,y)$.
    \end{quote} 

In this task, we will rigorously prove that this algorithm is correct. To do this, we will assume that there is some diameter $a \to b$ in $T$, and we aim to show that for any choice of $x$ that is among the furthest vertices of $r$, and any choice of $y$ among the furthest vertices from $x$, we must have that $d(x,y) = d(a,b)$.

\begin{enumerate}[label=(\alph*)]
    \item Show that if $x = a$, then $d(x,y) = d(a,b)$.

    \item Show that if $x \neq a$, and $r$ lies on the path from $a$ to $b$, then $d(x,y) = d(a,b)$.
    
    {\textbf{Hint:}} $T$ is acyclic, which implies the path from $x \to r$ cannot intersect with both the path from $r \to a$ and $r \to b$.
    
    \item Show that if $x \neq a$, and $r$ does not lie on the path from $a$ to $b$, then $d(x,y) = d(a,b)$.
    
     {\textbf{Hint:}} Consider a vertex $w$ that lies on the paths from $a \to b$, $r \to a$, and $r \to b$.   
     
    \item Hence, conclude that the path $x \to y$ is a diameter.
\end{enumerate}
\end{question}

\begin{rubric}
\begin{enumerate}
    \item Give a rigorous proof of the required statement.
    
    Expected length: A few short sentences.
    \item Give a rigorous proof of the required statement.
    
    Expected length: A paragraph.
    \item Give a rigorous proof of the required statement.
    
    Expected length: A couple of short paragraphs.
    \item Reach the required conclusion by using the statements proved in the 3 previous parts of the question.
    
    Expected length: A few short sentences.
\end{enumerate}
\end{rubric}

\begin{solution}
\end{solution}

\begin{attribution}
\end{attribution}

\end{document}